---
title: "Reproducible Research: Peer Assessment 1"
author: "Cliff Hayes"
output: html_document
html_document:
keep_md: true
---

##  Loading and preprocessing the data
### 1. Unzip and load data
```{r echo TRUE}
if (!file.exists("activity.csv")) {
    unzip('activity.zip')
}
activityData <- read.csv("activity.csv")
```
### 2. Convert date field to date class
```{r echo TRUE}
activityData$date <- as.Date(activityData$date, format = "%Y-%m-%d")
```
### 3. Convert 5 minute intervals to HH:MM format
```{r echo TRUE}
intAsChar <- as.character(activityData$interval)
activityData$interval <- sprintf("%04d", activityData$interval)
activityData$interval <- format(strptime(activityData$interval, format="%H%M"), format = "%H:%M")
```

## What is mean total number of steps taken per day?
```{r echo TRUE}
stepsPerDay <- aggregate(steps ~ date, activityData, sum)
```
### 1. Make a histogram of total number of steps taken per day
```{r echo TRUE}
library(ggplot2)
ggplot(stepsPerDay, aes(x = steps)) +
    geom_histogram(fill = "steelblue", binwidth = 1000) +
    scale_y_discrete(breaks = 1:10) +
    ggtitle("Histogram of Steps Taken per Day") +
    xlab("Number of Steps per Day") +
    ylab("Number of Days with X Steps") +
    theme_gray()
```
### 2. Calculate mean and median of total number of steps taken per day
```{r echo TRUE}
meanStepsPerDay <- round(mean(stepsPerDay$steps), digits = 0)
medianStepsPerDay <- round(median(stepsPerDay$steps), digits = 0)
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?

